Visual proteomics using whole-lamella 2D template matching

### 2022-03-21 manuscript.tex
Changes to montage processing [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/51095028c49de7986e39cc0ee234d0f6cdbddee1.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/51095028c49de7986e39cc0ee234d0f6cdbddee1/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2017398572

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/7e5fee3254041c2c66855e84f72b36c476ba1cb0/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/7e5fee3254041c2c66855e84f72b36c476ba1cb0}{jojoelfe/deco\_lace\_template\_matching\_manuscript@7e5fee3}
on March 9, 2022.

>>>>

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/51095028c49de7986e39cc0ee234d0f6cdbddee1/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/51095028c49de7986e39cc0ee234d0f6cdbddee1}{jojoelfe/deco\_lace\_template\_matching\_manuscript@5109502}
on March 21, 2022.
